Temporal Activity Detection in Untrimmed Videos with Recurrent Neural Networks

### 2016-10-15 paper.tex
Things

We propose a simple pipeline which can be able to perform well in classification and temporal localization on activities on videos.
Moreover, the flexibility of this sequence to sequence prediction allows the proposed network to face tasks where more than a single activity is present in the video.

% ALBERTO: que més explico a les conclusions

>>>>

We propose a simple pipeline which can be able to perform well in classification and temporal localization on activities on videos.
Moreover, the flexibility of this network performing a sequence to sequence prediction allows it to face tasks where more than a single activity is present in the video.

% ALBERTO: que més explico a les conclusions???
